Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-08-23 doc/paper-lcr.tex
paper changes

Throughout this paper magnitudes are given in the AB system \citep{Oke74} and
we adopt standard ``concordance'' parameters for our reference cosmology, \ie
$h=0.7$, $\Omega_m=0.3$ and $\Omega_\Lambda=0.7$, where the symbols indicate
the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
dark energy density of the Universe in units of the critical density
\citep[e.g.\ ][]{Kom++09}.

@@

If the intrinsic source brightness changes, the observed brightness in each image does not change
simultaneously - there is a time delay, $\Delta t$, between the brightness change in
each image. Despite the invariance of the image positions and fluxes, under the addition
of an external convergence the relative Fermat potential between the images is {\it not}
invariant, and so the time delay changes. As such it is necessary to include $\kappax$
in our lens modelling, if cosmological parameters are to be estimated accurately and
precisely from observed time delays \citep{suyu2010}.

@@

Disturbingly, if one integrates the density profile of an NFW profile, the total mass is divergent.
Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
line sight will also be divergant\footnote{At large radius, $\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos centred within an annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically}.Since infinite mass is unphysical, the profile must be truncated at some point. \flag{previous truncation results}. Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius. In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
\be\label{eq:bmoprofile}
\rho(r) = 
\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
\ee
which is the same as the NFW profile in the limit that $r_t$ goes to infinity. Defining $x$ as the dimensionless projected radial distance $R/r_{s}$ and $\tau$ as the dimensionless truncation radius $r_{t}/r_{s}$, \citet{BMO} derives the projected mass density, which is given by:
\begin{align}\label{eq:kappaBMO}
\Sigma_{\rm}(x) = {2\tau^2 \over (\tau^2+1)^2}\left(
        {\tau^2+1\over x^2-1}\left(1-\mathcal{F}(x)\right)
        +
        2\mathcal{F}(x)\right.\nonumber\\
        -
        \left. {\pi \over \sqrt{\tau^2+x^2}}
        +
        {(\tau^2-1)\mathcal{L}(x,\tau)
        \over
        \tau\sqrt{\tau^2+x^2}}\right)
\end{align}
where $\mathcal{F}(x)$ and $\mathcal{L}(x,\tau)$ are defined as
\be\label{eq:F} 
\mathcal{F}(x) \equiv \begin{cases}  \frac{{\rm cos}^{-1} (1/x)}{\sqrt{x^2-1}} \hspace{0.2cm} & (x>1) \\
\\
\frac{4-x^2}{3}  & (x=1)\\
\\
\frac{ {\rm cosh}^{-1} (1/x)}{\sqrt{1-x^2}} & (x<1)
\end{cases}
\ee
\be\label{eq:L}
\mathcal{L}(x,\tau) = \ln\left(\frac{x}{\sqrt{\tau^2+x^2}+\tau}\right)
\ee
%the convergence is given by $\Sigma_{\rm BMO}(x) / \Sigma_{\rm cr}(z)$.

@@

Given the halo mass catalogue from the Millenium Simulation, and convergence maps produced by
ray-tracing through the MS's n-body particles, 
it is possible to test the validity of the prescription outlined in Section \ref{sec:model}. We do this
using $\kapparay$ as a proxy for $\kappatrue$. The reconstruction prescription is tested given perfect
knowledge of the halos' virial masses and redshifts; this provides us with a measure of the intrinsic
errors induced by treating matter as truncated NFW halos. To quantify this 10000 lines of sight are chosen
from random positions in the catalogue, and for each line of sight we reconstruct the
convergences from every halo within 5 arcminutes and compare the reconstructed
kappas with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ 
shown in Figure \ref{fig:ScattervsTruncation}. It is clear from Figure \ref{fig:ScattervsTruncation} 
that as long as the truncation is greater than a few virial radii, the choice of truncation
radius does not broadly affect the scatter on $\kapparay-\kapparec$; from now on we choose 
to truncate the halos at $10 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
 as the intrinsic error of the prescription. The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Whilst we do not
focus on shear in this work, such outliers would likely be rejected by their reconstructed shear not matching the
shear of the lens model (see \citet{wong} for the practicalities of this), this makes our estimate of the intrinsic error pessimistic.

\begin{figure}\label{fig:ScattervsTruncation}
\includegraphics[width=\columnwidth]{truncation_scatter.eps}
\caption[magcut]{}
\end{figure}

\tom{this paragraph is phrased badly}
If $\kapparec$ is to be used in a real survey it is important that it is not a biased estimator of the true $\kappax$. 
Ideally one wants $\langle \kapparec-\kappatrue \rangle$ to equal 0 and $\kapparec-\kappatrue$ to be independant of
$\kapparec$., since the void correction ensures $\langle \kapparec \rangle = 0$ any bias in $\langle \kapparec-\kapparay \rangle$ comes
from the variations in $\kapparay$. With 8.2$\times 10^8$ pixels, uniformly spaced over 196 deg$^2$ of simulated sky,
 $\langle \kapparay \rangle$ = -0.00014. However, it is improbable that such a large number of lines of sight
 could be reconstructed in reality and the mean of $\kappatrue$ for a small subset of sightlines will not necessarily
equal zero. We find this error to be
\be\label{eq:sigmav}
\sigma(\kappav) \simeq 0.036 / N^{\frac{1}{2}},
\ee
 where $N$ is the number of lines of sight, although $\pr(\kappav)$ has positive skew for small $N$.
 Care must be taken that the callibration lines of sight are not biased in $\kappax$ or the final $\pr(\kappav)$ will also be biased. For the rest of this work we use 1000  randomly chosen calibration lines of sight to calculate $\kappav$, introducing an error on $\kappax$ of $0.001$. 1000 callibration lines of sight is unfeasable currently, but should be reasonable in the LSST era. Since the true $\langle \kapparay \rangle$ = -0.00014 is two orders of magnitude smaller than intrinsic error of the halo prescription, $\kapparec$ can be seen as unbiased given a large enough sample of lines of sight and Figure \ref{fig:bias} shows that there is no statistically significant evidence that $\kapparec$ is a biased estimator, regardless of the individual value of $\kapparec$.

\begin{figure}\label{fig:isitbiased}
\includegraphics[width=\columnwidth]{isitbiased.eps}
\caption[Biased?]{}
\end{figure}
\begin{figure}\label{fig:magcut}
\includegraphics[width=\columnwidth]{mag_scatter.eps}
\caption[magcut]{}
\end{figure}
\begin{figure}\label{fig:radcut}
\includegraphics[width=\columnwidth]{radius_scatter.eps}
\caption[radius cut]{}
\end{figure}

The error from the void correction, and the intrinsic error from the halo based prescription are unavoidable errors, even with perfect knowledge of halo mass and position. Before investigating the errors caused by imperfect knowledge of halo mass and redshift, we investigate the errors induced by a magnitude limited reconstruction and a field of view limited reconstruction. The halos in our catalogue are given magnitudes by the semi-analytic model of \citet{SAM} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos. The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24. Figure \ref{fig:magcut} shows that the width of $\kapparec-\kapparay$ decreases quickly between $i=18$ and $i=24$. Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence. Objects fainter than $i=24$ are too small to be important unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$ - it is likely that these ultra-faint halos (or substructures) are the major source of the scatter in $\kapparec-\kapparay$, but a deeper survey will not be sufficient to decrease the size of this scatter. Since a large number of callibration lines of sight are needed to shrink the width of $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes. \citet{Auger2007} showed that the majority significant perturbers are within 15 arcseconds of the lens. Figure \ref{fig:radcut} shows the width of $\kapparec-\kapparay$ as a function of reconstruction radius; in almost all cases there is no significant contribution to $\kappa$ from halos that are centred more than 1 arcminute away, although large groups or clusters can sometimes still make a contribution as far out as four arcminutes. For the rest of this work we will continue to model all of the halos out to 5 arminutes with an $i$ magnitude greater than 26, although a reconstruction with fields going out to two arcminutes and down to $i<24$ would do almost as well.

@@

Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halo, 
and will likely not have access to their spectroscopic redshift either. Instead these properties must be inferred from astrophysical
observables. In principle the only observables are astrometric positions, photometric colours and possibly spectra. In this section we
quantify the errors induced by inferring the halo mass and redshift from the observables. Much work has already focused on using
photometric colours to infer stellar mass \citep[\eg][]{augerstellarpops} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
of $\kappax$. We will investigate three main sources of error: inferring halo mass given observed stellar mass; halos at the wrong redshift
due to photometric redshift error, and; the combination of both redshift and stellar mass errors.

Consider three sources of scatter in the halo model: zphot, Mstar|zphot, and
Mhalo|Mstar,zphot. Mechanism for including scatter in model: draw samples from
PDFs. Result is not one predicted kappa, but one P(kappa) for each lightcone.
This is what is required by single-lens analyses.

@@

We thank Risa Wechsler and Peter Behroozi for useful discussions and 
suggestions.
\input{acknowledgments.tex}

@@

>>>>

Throughout this paper magnitudes are given in the AB system \citep{Oke74} and
we adopt the Millenium Simulation's ``concordance'' parameters for our reference cosmology, \ie
$h=0.73$, $\Omega_m=0.25$ and $\Omega_\Lambda=0.75$, where the symbols indicate
the Hubble Constant in units of 100 km s$^{-1}$ Mpc$^{-1}$ and the matter and
dark energy density of the Universe in units of the critical density
.%\citep[e.g.\ ][]{Kom++09}.

@@

If the intrinsic source brightness changes, the observed brightness in each image does not change
simultaneously - there is a time delay, $\Delta t$, between the brightness change in
each image. Despite the invariance of the image positions and fluxes, under the addition
of an external convergence (and appropriate re-scaling of the lens potential) the relative Fermat potential between the images is {\it not}
invariant, and so the time delay changes. As such it is necessary to include $\kappax$
in the lens modelling, if cosmological parameters are to be estimated accurately and
precisely from observed time delays \citep{suyu2010}.

@@

Unphysically, if one integrates the density profile of an NFW profile, the total mass is divergent.
Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos centred within an annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically}. Since infinite mass is unphysical, the profile must be truncated at some point. \flag{previous truncation results}. Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low; \citet{Nandra2012} showed that the Universe's expansion can place an upper limit on the radius of NFW halos -- for cluster scale halos, this happens at around 25 times the NFW scale radius. In \Sref{sec:knownMh+z} we investigate how different truncations affect the recovered total convergence for a line of sight, using the truncated NFW profile of \citet{BMO}
\be\label{eq:bmoprofile}
\rho(r) = 
\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
\ee
which is the same as the NFW profile in the limit that $r_t$ goes to infinity. The convergence and shear for the BMO profile are given in Appendix \ref{appendix:halos}.

@@

Given the halo mass catalogue from the Millenium Simulation, and convergence maps produced by
ray-tracing through the MS's n-body particles, 
it is possible to test the validity of the prescription outlined in Section \ref{sec:model}. We do this
using $\kapparay$ as a proxy for $\kappatrue$. The reconstruction prescription is tested given perfect
knowledge of the halos' virial masses and redshifts; this provides us with a measure of the intrinsic
errors induced by treating matter as truncated NFW halos. To quantify this 10000 lines of sight are chosen
from random positions in the catalogue, and for each line of sight we reconstruct the
convergences from every halo within 5 arcminutes and compare the reconstructed
kappas with those from the ray tracing results. The standard deviation on $\kapparay$-$\kapparec$ 
shown in Figure \ref{fig:ScattervsTruncation}. It is clear from Figure \ref{fig:ScattervsTruncation} 
that as long as the truncation is greater than a few virial radii, the choice of truncation
radius does not broadly affect the scatter on $\kapparay-\kapparec$; from now on we choose 
to truncate the halos at $5 \Rhalo$. Since $\sigma\left(\kapparay-\kapparec\right)$ does not go to
zero, it is clear that out halo based prescription does not perfectly replicate the n-body results, we refer to this
 as the intrinsic error of the prescription. The intrinsic error has a standard deviation of $\sigi \sim 0.018$, although
this figure is inflated by a few outliers in the tails of $\pr\left(\kapparay-\kapparec\right)$. Whilst we do not
focus on shear in this work, such outliers would likely be rejected by their reconstructed shear not matching the
shear of the lens model (see \citet{wong} for the practicalities of this), this makes our estimate of the intrinsic error pessimistic.

\begin{figure}
\includegraphics[width=\columnwidth]{truncation_scatter.eps}
\caption[magcut]{}
\label{fig:ScattervsTruncation}
\end{figure}

\tom{this paragraph is phrased badly}
If $\kapparec$ is to be used in a real survey it is important that it is not a biased estimator of the true $\kappax$. 
Ideally one wants $\langle \kapparec-\kappatrue \rangle$ to equal 0 and $\kapparec-\kappatrue$ to be independant of
$\kapparec$., since the void correction ensures $\langle \kapparec \rangle = 0$ any bias in $\langle \kapparec-\kapparay \rangle$ comes
from the variations in $\kapparay$. With 8.2$\times 10^8$ pixels, uniformly spaced over 196 deg$^2$ of simulated sky,
 $\langle \kapparay \rangle$ = -0.00014. However, it is improbable that such a large number of lines of sight
 could be reconstructed in reality and the mean of $\kappatrue$ for a small subset of sightlines will not necessarily
equal zero. We find this error to be
\be\label{eq:sigmav}
\sigma(\kappav) \simeq 0.036 / N^{\frac{1}{2}},
\ee
 where $N$ is the number of lines of sight, although $\pr(\kappav)$ has positive skew for small $N$.
 Care must be taken that the callibration lines of sight are not biased in $\kappax$ or the final $\pr(\kappav)$ will also be biased. For the rest of this work we use 1000  randomly chosen calibration lines of sight to calculate $\kappav$, introducing an error on $\kappax$ of $0.001$. 1000 callibration lines of sight is unfeasable currently, but should be reasonable in the LSST era. Since the true $\langle \kapparay \rangle$ = -0.00014 is two orders of magnitude smaller than intrinsic error of the halo prescription, $\kapparec$ can be seen as unbiased given a large enough sample of lines of sight. However since $\kappax$ reconstruction based on perfect knowledge of the halo mass and position is unrealistic we must re-visit the question of bias in Section \ref{sec:obsMstar+z}, using more realistic observables.

\comment{
 and Figure \ref{fig:bias} shows that there is no statistically significant evidence that $\kapparec$ is a biased estimator, regardless of the individual value of $\kapparec$.

\begin{figure}
\includegraphics[width=\columnwidth]{isitbiased.eps}
\caption[Biased?]{}
\label{fig:isitbiased}
\end{figure}
}
\begin{figure}
\includegraphics[width=\columnwidth]{mag_scatter.eps}
\caption[magcut]{}
\label{fig:magcut}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{radius_scatter.eps}
\caption[radius cut]{}
\label{fig:radcut}
\end{figure}

The error from the void correction, and the intrinsic error from the halo based prescription are unavoidable errors, even with perfect knowledge of halo mass and position. Before investigating the errors caused by imperfect knowledge of halo mass and redshift, we investigate the errors induced by a magnitude limited reconstruction and a field of view limited reconstruction. The halos in our catalogue are given magnitudes by the semi-analytic model of \citet{SAM} and by applying magnitude cuts to our catalogue, we can investigate the scatter caused by unobserved halos. The majority of the convergence comes from halos with an $i$ magnitude between 18 and 24. Figure \ref{fig:magcut} shows that the width of $\kapparec-\kapparay$ decreases quickly between $i=18$ and $i=24$. Objects brighter than $i=18$ are either too rare or too close to the observer to make a significant contribution to the convergence. Objects fainter than $i=24$ are too small to be important unless they are extremely close to the line of sight where it is likely that neglecting stellar mass and using a spherical NFW prescription are too naive to adequately reconstruct $\kappax$ - it is likely that these ultra-faint halos (or substructures) are the major source of the scatter in $\kapparec-\kapparay$, but a deeper survey will not be sufficient to decrease the size of this scatter. Since a large number of callibration lines of sight are needed to shrink the width of $\pr(\kappav)$, it may prove unrealistic to reconstruct the calibration lines of sight out to 5 arcminutes. Figure \ref{fig:radcut} shows the width of $\kapparec-\kapparay$ as a function of reconstruction radius; in almost all cases there is no significant contribution to $\kappa$ from halos that are centred more than 1 arcminute away, although large groups or clusters can sometimes still make a contribution as far out as four arcminutes. For the rest of this work we will continue to model all of the halos out to 5 arminutes with an $i$ magnitude greater than 26, although a reconstruction with fields going out to two arcminutes and down to $i=24$ would do almost as well.

@@

Real attempts to reconstruct the convergence along a line of sight will not have direct access to the masses of dark matter halo, 
and will likely not have access to their spectroscopic redshift either. Instead these properties must be inferred from astrophysical
observables. In principle the only observables are astrometric positions, photometric colours and possibly spectra. In this section we
quantify the errors induced by inferring the halo mass and redshift from the observables. Much work has already focused on using
photometric colours to infer stellar mass \citep[\eg][]{xxx} and redshifts \citep[\eg][]{BPZ}, in line with these we shall use
stellar mass and photometric redshifts (with appropriate errors), as the observables that must be converted into an estimate
of $\kappax$. We will investigate three main sources of error: inferring halo mass given observed stellar mass; halos at the wrong redshift
due to photometric redshift error, and; the combination of both redshift and stellar mass errors.

We generate a stellar mass for each halo according to the stellar mass--halo mass relation of \citet{behroozi2010}. From this stellar mass we simulate 
an observed stellar mass by drawing a sample from $\pr(\log(M_{* \mathrm {obs}})|\log(M_{* \mathrm {true}}))$ which is given by the product of the galaxy stellar mass function (GSMF) of \citet{Fontana2006} and a Gaussian of width $\sigma_{M_*}$ centred on $\log(M*_{\mathrm {true}})$. Where a spectroscopic redshift exists stellar masses can be estimated with typical uncertainties of 0.15 dex \citep{xxx}, however with photometric redshifts stellar mass uncertainties are typically three times as large \citep{xxx}; we use $\sigma_{M_*}=0.15$ for halos with a spectroscopic redshift and $\sigma_{M_*}=0.45$ otherwise. The \citet{Fontana2006} GSMF is given by a Schechter function with redshift evolving parameters
\be
\label{eq:GSMF}
{\dee N \over \dee M_*} \propto \left(10^{(M_*-M_0(z))}\right)^{(1+\alpha(z))} \exp \left(-10^{(M_*-M_0(z))}\right)
\ee 
where $M_0(z)=11.16+0.17z-0.07z^2$ and $\alpha(z)=-1.18-0.082z$. For photometric redshift errors we draw a redshift from $\pr(z_{\rm true}|z_{\rm obs})$ which we take as a Gaussian of width $0.1(1+z_{\rm spec})$ centred on $z_{\rm spec}$, where $z_{\rm spec}$ is the halo's true redshift in \MS catalogue

\begin{figure}
\includegraphics[width=\columnwidth]{widthvkappa.eps}
\caption[radius cut]{}
\label{fig:width}
\end{figure}

Our results are summarized in Figure \ref{fig:width}. We reconstruct 10000 lines of sight and each of the reconstructed $\pr(\kappa)$ is summarized by their mean $\kapparec$, and their width containing $68\%$ of the probability, $\sigt$. Reconstructing the lines of sight with perfect knowledge of the redshift but an uncertain stellar mass, we find that $\sigt$ grows with $\kapparec$; this is not surprising since the low $\kapparec$ lines of sight are relatively empty and so there are few opportunities for uncertainties in the halo masses to propogate into $\kapparec$ uncertainties. Our results are well fit by a straight line given by 
\be
\sigt=0.012+0.26 \langle\kapparec\rangle;
\label{eq:Mstarfit}
\ee
this is the reconstruction error that could be expected from a complete spectroscopic survey of the field. A complete spetroscopic survey is unrealistic, but Equation \ref{eq:Mstarfit} represents a lower limit on the reconstruction error.
We find that with a perfect knowledge of the halo mass, but photometric redshifts the reconstructed $\pr(\kappa)$ has a mean $\sigt$ of 0.003. For the lines of sight with $\kapparec {\rm s}$ that are dominated by a single significant perturber the photometric redshift error can induce a larger uncertainty on $\kapparec$, but only $2.9 \%$ of sightlines have $\sigt > 0.01$; typical photometric redshift errors do not propogate into a significant uncertainties on $\kapparec$ if the halo mass is known. This is seen in Figure \ref{fig:width}, $\sigt$ is typically much larger for the perfect redshift reconstructions than the perfect mass reconstructions. The results are well fit by
\be
\sigt=0.0025+0.041\langle\kapparec\rangle
\label{eq:photozfit}
\ee
Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise. In principle the photometric redshift is correlated with the infered stellar mass however we do not model this since the redshift error produces a small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.  For the reconstructions with imperfect redshift and stellar mass the resulting uncertainty is significantly larger than the quadrature sum of the $\sigt {\rm s}$ in Equations \ref{eq:Mstarfit} and \ref{eq:photozfit}, this is because the uncertain redshift propogates into a broadened $\pr(M_{*})$. The  
ns than the perfect mass reconstructions. For a complete photometric survey down to $i=26$ our reconstructions are fit by the line
\be
\sigt=0.026+0.037\langle\kapparec\rangle
\label{eq:bothfit}
\ee
The fits are shown on Figure \ref{fig:intrinsicvsreconstruction}, where we compare the reconstruction errors with typical size of the intrinsic error from Section \ref{sec:knownMh+z}. With photometric redshifts only, the reconstruction error is typically half the size of the intrinsic error, but for a survey with complete spectroscopic coverage the two errors are of similar size. The photometric results can be greatly improved by the addition of spectroscopic redshifts for a small number of halos. Photometric redshifts are sufficient to estimate the $\kappa$ contribution from each halo; once this is know the most important halos can be targeted for spectroscopic follow-up. It is not always possible to get a spectroscopic redshift for faint objects, as such we use spectroscopic redshifts for galaxies with $i<24$ that the sitting in halos that individually contribute $\kappa>0.0005$. This selection corresponds to an average of $12 \pm 4$ galaxies per line of sight for which spectra are needed; the number of spectra needed per line of sight is shown as a histogram in Figure \ref{fig:spechist}. Such a spectroscopic survey yields only a modest improvement upon the purely photometric case being well fit by 
\be
\sigt=+\langle\kapparec\rangle
\label{eq:spec1fit}
\ee
This modest improvent appears counter intuitive, since spectra for all the subset of halos with $i<24, \kappat>0.0005$ halos contains the majority of the total $\kappax$ along alomst all lines of sight. The lack of significant improvement comes 
from the many massive halos that are intermediate distances from the line of sight; they do not contribute significantly to the true $\kappax$, but without spectroscopic reshifts their highly uncertain stellar masses propogate into broad $\pr(\Mhalo)$ and into small probability of large individual $\kappa$ contributions; since there are typically several hundred such objects within 5 arcminutes of the line of sight, their net contribution dominates the width of the photometrically generated $\pr(\kappax)$. However since massive objects are typically bright it is realtively fast to obtain their spectra with an 8~m class telescope. Galaxies with $i<22, \kappat>0.000001$ corresponds to roughly $200 \pm 100$ objects per line of sight; with spectroscopic redshifts for all of these plus the $i<24, \kappat>0.0005$ objects the reconstruction is greatly improved, being fit by
\be
\sigt=+\langle\kapparec\rangle
\label{eq:spec1fit}
\ee
The case of complete photometric coverage and partial spectroscopic coverage is closest to what might be expected from a real reconstruction of a field. We will refer to this as the 'hybrid' case for the rest of this paper, where all galaxies with $i<22, \kappat>0.000001$ or $i<24, \kappat>0.0005$ have spectra, but no others.

In Figure \ref{fig:intrinsicvsreconstruction} we show all of the fits, and compare them to the typical size of the difference between the ray-traced $\kapparay$ and the mean of the reconstructed $\kapparec$ which is a good measure of the intrinisic error in the reconstruction. For the purely photometric reconstruction $\sigt$ is larger than 98 percent of $|\kapparay - \langle \kapparec \rangle |$ indicating that the reconstruction is the dominant source of error. For the purely spectroscopic reconstruction $\sigt$ is larger than 44 percent of $|\kapparay - \langle \kapparec \rangle |$; the intrinsic error is slightly larger than the reconstruction error. For the hybrid case $\sigt$ is larger than 88 percent of $|\kapparay - \langle \kapparec \rangle |$, indicating that the intrinsic error is a sub-dominant effect.

Since the reconstruction does not produce a symmetric $\pr(\kappax)$, we must take care in ensuring that the reconstruction has not biased $\langle \kapparec \rangle $ as an estimator of $\kapparay$. Figure 12 al

\begin{figure}
\includegraphics[width=\columnwidth]{spechist.eps}
\caption[spechist]{}
\label{fig:spechist}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{intrinsicvsreconstruction.eps}
\caption[radius cut]{}
\label{fig:intrinsicvsreconstruction}
\end{figure}

@@

TC thanks Vasily Belokurov for guidance and discussions.
We thank Risa Wechsler and Peter Behroozi for useful discussions and 
suggestions.
\input{acknowledgments.tex}

@@

 Defining $x$ as the dimensionless projected radial distance $R/r_{s}$ and $\tau$ as the dimensionless truncation radius $r_{t}/r_{s}$, \citet{BMO} derives the projected mass density, which is given by:
\begin{align}\label{eq:kappaBMO}
\Sigma_{\rm}(x) = {2\tau^2 \over (\tau^2+1)^2}\left(
        {\tau^2+1\over x^2-1}\left(1-\mathcal{F}(x)\right)
        +
        2\mathcal{F}(x)\right.\nonumber\\
        -
        \left. {\pi \over \sqrt{\tau^2+x^2}}
        +
        {(\tau^2-1)\mathcal{L}(x,\tau)
        \over
        \tau\sqrt{\tau^2+x^2}}\right)
\end{align}
where $\mathcal{F}(x)$ and $\mathcal{L}(x,\tau)$ are defined as
\be\label{eq:F} 
\mathcal{F}(x) \equiv \begin{cases}  \frac{{\rm cos}^{-1} (1/x)}{\sqrt{x^2-1}} \hspace{0.2cm} & (x>1) \\
\\
\frac{4-x^2}{3}  & (x=1)\\
\\
\frac{ {\rm cosh}^{-1} (1/x)}{\sqrt{1-x^2}} & (x<1)
\end{cases}
\ee
\be\label{eq:L}
\mathcal{L}(x,\tau) = \ln\left(\frac{x}{\sqrt{\tau^2+x^2}+\tau}\right)
\ee
%the convergence is given by $\Sigma_{\rm BMO}(x) / \Sigma_{\rm cr}(z)$.

\flag{SHEAR HERE}
